---
title: "Comparison R and C++"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{compare_R_and_Cpp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Introduction
This vignette demonstrates the correctness and efficiency comparison between the R and C++ implementations of functions in the `newHyu625Hw3` package. The comparisons are made using the `bench` and `all.equal` functions.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(newHyu625Hw3)
library(bench)
```

##Comparison Check

#1 Count_pairs
#Correctness check
```{r}
n <- 100
m <- 2

# R implementation
result_r <- count_pairs(n, m)

# C++ implementation
result_cpp <- count_pairs_cpp(n, m)

# Check correctness
all.equal(result_r, result_cpp)


```
#Performance Comparison
```{r}
bench::mark(
  R_version = count_pairs(n, m),
  Cpp_version = count_pairs_cpp(n, m)
)

```
##2 Gen_logit
#Correctness Check
```{r}
matrix_1 <- matrix(rnorm(10), nrow = 2)
x <- rnorm(5)

# R implementation
result_r <- gen_logit(matrix_1, x)

# C++ implementation
result_cpp <- gen_logit_cpp(matrix_1, x)

# Check correctness
all.equal(result_r, result_cpp)

```
#Performance Comparison
```{r}
# Ensure data validity
matrix_1 <- matrix(rnorm(10), nrow = 2)
x <- rnorm(5)
stopifnot(all(is.finite(matrix_1)))
stopifnot(all(is.finite(x)))

# R implementation
result_r <- gen_logit(matrix_1, x)

# C++ implementation
result_cpp <- gen_logit_cpp(matrix_1, x)

# Correctness check
all.equal(result_r, result_cpp)

# Performance comparison
bench::mark(
  R_version = gen_logit(matrix_1, x),
  Cpp_version = gen_logit_cpp(matrix_1, x)
)

```

##3 Matrix_kendall
#Correctness Check
```{r}
set.seed(123)
X <- matrix(runif(1000), nrow = 100, ncol = 10)

# R implementation
result_r <- matrix_kendall(X)

# C++ implementation
result_cpp <- matrix_kendall_cpp(X)

# Check correctness
all.equal(result_r, result_cpp)

```
#Performance Comparison
```{r}
bench::mark(
  R_version = matrix_kendall(X),
  Cpp_version = matrix_kendall_cpp(X)
)

```
##4 Num_str
#Correctness Check
```{r}
input_num <- "12345"

# R implementation
result_r <- num_str(input_num)

# C++ implementation
result_cpp <- num_str_cpp(input_num)

# Check correctness
all.equal(result_r, result_cpp)

```
#Performance Comparison
```{r}
bench::mark(
  R_version = num_str(input_num),
  Cpp_version = num_str_cpp(input_num)
)

```

##5 Quadratic
#Correctness Check
```{r}
a <- 1
b <- -3
c <- 2

# R implementation
result_r <- quadratic(a, b, c)

# C++ implementation
result_cpp <- quadratic_cpp(a, b, c)

# Check correctness
all.equal(result_r, result_cpp)

```
#Performance Comparison
```{r}
bench::mark(
  R_version = quadratic(a, b, c),
  Cpp_version = quadratic_cpp(a, b, c)
)

```

##6 Triangle
#Correctness Check
```{r}
edges <- matrix(c(1, 2, 2, 3, 3, 1), byrow = TRUE, ncol = 2)

# R implementation
result_r <- triangle(edges)

# C++ implementation
result_cpp <- triangle_cpp(edges)

# Check correctness
all.equal(result_r, result_cpp)

```
#Performance Comparison
```{r}
bench::mark(
  R_version = triangle(edges),
  Cpp_version = triangle_cpp(edges)
)

```


##Conclusion
This vignette showcases how the C++ implementations in this package deliver results identical to their R counterparts while offering substantial performance enhancements. These improvements make the package highly efficient for handling computationally demanding tasks.
