---
title: "Introduction to hyu625hw3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Overview

The `hyu625hw3` package provides a collection of functions for statistical modeling, mathematical computations, and graph analysis. This vignette demonstrates the usage of each function and compares its performance with alternative approaches where applicable.

---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(newHyu625Hw3)
```


## 1. Count Pairs
The `count_pairs()` function counts integer pairs `(x, y)` in `{1, 2, ..., n}` such that \(xy \mod (x + y) = m\).

# Example Usage
```{r count_pairs_example}
# Example: Count pairs for n=3 and m=1
result <- count_pairs(3, 1)
print(result)
```
##Performance Comparison
```{r}
library(bench)

# Benchmarking
bench::mark(
  custom = count_pairs(100, 5),
  base = sum(outer(1:100, 1:100, FUN = function(x, y) (x * y) %% (x + y) == 5))
)

```

## 2. Generalized Logit
The gen_logit() function calculates probabilities for each level in a generalized logit model.
#Example Usage
```{r}
matrix_1 <- matrix(c(1, 0, 0, 1), nrow = 2)
x <- c(0.5, 0.8)

# Calculate probabilities
probs <- gen_logit(matrix_1, x)
print(probs)

```
#Performance Comparison
```{r}
library(bench)

# Example inputs
matrix_1 <- matrix(c(1, 0, 0, 1), nrow = 2)
x <- c(0.5, 0.8)

base_gen_logit <- function(matrix_1, x) {
  K <- nrow(matrix_1)  # Number of categories (excluding reference level 0)
  linear_preds <- apply(matrix_1, 1, function(row) sum(row * x))  # Linear predictors
  exp_values <- exp(linear_preds)  # Exponentiated linear predictors
  probs <- c(1, exp_values) / (1 + sum(exp_values))  # Probabilities for all levels
  probs
}


bench::mark(
  custom = gen_logit(matrix_1, x),
  base = base_gen_logit(matrix_1, x)
)



```

## 3. Matrix Kendall
The matrix_kendall() function computes Kendall's τ for each row of a matrix compared to a ranking vector y.

# Example Usage
```{r}
X <- matrix(c(1, 2, 3, 2, 3, 1), nrow = 2, byrow = TRUE)

# Compute Kendall's τ
max_tau <- matrix_kendall(X)
print(max_tau)

```
#Performance Comparison
```{r}
library(bench)

# Example input
X <- matrix(c(1, 2, 3, 2, 3, 1), nrow = 2, byrow = TRUE)
y <- 1:ncol(X)

# Benchmarking matrix_kendall() against a base R loop approach
bench::mark(
  custom = matrix_kendall(X),
  base = max(apply(X, 1, function(row) cor(row, y, method = "kendall")))
)

```

## 4. Number string 
The num_str() function finds the first position of a given sequence of digits in an infinite concatenated string of natural numbers.
#Example Usage
```{r}
# Find the first occurrence of "12"
num_str("12")
```
#Performance Comparison
```{r}
library(bench)

# Example input
input_num <- "12"

base_result <- {
  s <- paste0(1:10000, collapse = "")
  regexpr("12", s)[1]  # Extracts the first position directly
}

bench::mark(
  custom = num_str("12"),
  base = {
    s <- paste0(1:10000, collapse = "")
    regexpr("12", s)[1]
  }
)
```

## 5. Quadratic Equation Solver
The quadratic() function solves a quadratic equation and returns the smallest solution.
#Example Usage
```{r}
# Solve the equation x^2 + 4x + 1 = 0
solution <- quadratic(1, 4, 1)
print(solution)
```
#Performance Comparison
```{r}
library(bench)

# Example input
a <- 1
b <- 4
c <- 1

# Benchmarking quadratic() against a simplified direct solution
bench::mark(
  custom = quadratic(a, b, c),
  base = {
    delta <- b^2 - 4 * a * c
    if (delta >= 0) min((-b + c(sqrt(delta), -sqrt(delta))) / (2 * a))
  }
)
```

## 6. Triangle Finder
The triangle() function checks whether a given undirected graph (represented as a matrix of edges) contains any triangles.
#Example Usage
```{r}
edges <- matrix(c(1, 2, 2, 3, 3, 1), nrow = 3, byrow = TRUE)

# Check for triangles
has_triangle <- triangle(edges)
print(has_triangle)

```
#Performance Comparison
```{r}
library(bench)

# Example input
edges <- matrix(c(1, 2, 2, 3, 3, 1), nrow = 3, byrow = TRUE)

# Benchmarking triangle() against an adjacency matrix approach
bench::mark(
  custom = triangle(edges),
  base = {
    nodes <- unique(c(edges))
    adj <- matrix(0, nrow = length(nodes), ncol = length(nodes))
    for (i in 1:nrow(edges)) {
      adj[edges[i, 1], edges[i, 2]] <- 1
      adj[edges[i, 2], edges[i, 1]] <- 1
    }
    any(rowSums(adj %*% adj > 0 & adj) > 0)
  }
)

```
##Use of the sample dataset for each function in this package
```{r}
##Count pairs
result <- count_pairs(example_count_pairs[[1]]$n, example_count_pairs[[1]]$m)
print(result)

## Gen logit 
logit_result <- gen_logit(example_gen_logit[[1]]$matrix_1, example_gen_logit[[1]]$x)
print(logit_result)

## Matrix kendall
result_matrix_kendall <- matrix_kendall(example_matrix_kendall[[1]])
print(result_matrix_kendall)

## Num str
result_num_str <- num_str(example_num_str[1])
print(result_num_str)

## Quadratic

result_quadratic <- quadratic(example_quadratic[[1]]$a, example_quadratic[[1]]$b, example_quadratic[[1]]$c)
print(result_quadratic)

## Triangle 
triangle_result <- triangle(example_triangle[[1]])
print(triangle_result)

```




###Conclusion
This vignette showcases the features and capabilities of this package. Each function is illustrated with practical examples, and performance comparisons are provided when relevant.

